\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/BadUSBC.tex
nits
Update introduction
pass on abstract

\begin{abstract}
The security of USB protocol has been paid extensive attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted extensive experiments and a user study on a real-life attack scenario.
10 volunteers are involved in, and 4,796 of 94,058 records obtained by \tool in the user study are related to privacy information.
\fengwei{What results?}
%\fengwei{what countermeasures do we propose? including isolated UI rendering.}
We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
\end{abstract}

@@

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}
\balance

>>>>

\begin{abstract}

The security of USB protocol has been paid extensive attention to, despite its
    wide usage.  Due to the \textit{trust-by-default} characteristics, USB
    security has caused serious problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising normal USB devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of user interface to conduct precise attacks, and they
    can detected by multiple existing countermeasures.  In this work, we
    extended BadUSB to support the new features of USB Type-C and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more
    precise and effective, and also bypasses existing defense methods for
    BadUSB.  To the best of our knowledge, \tool is the first attack model
    utilizing USB Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,796 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed our recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.

\end{abstract}

@@

\balance

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}
